### 2013-05-16 draft.tex
edited thin section paragraph, electron microscopy section

While all fossils were inspected under a microscope prior to sampling, we were not able to inspect all fossils in thin section, because carbonate clumped isotope measurements require large amounts of material, some of which is lost during preparation of thin sections. However, two representative brachiopods and rugose corals were examined in thin section. 30 $\mu$m-thick uncovered, polished thin sections were obtained from cuts through the fossils. These thin sections were examined first in transmitted and reflected light to characterize calcite textures, and were then characterized using several different spectroscopic techniques, described below.

@@

For electron backscatter diffraction (EBSD),  The thin sections were analyzed using the same SEM as above, under variable pressure vacuum, with an electron high tension of 20 kV. The stage was tilted 70$^{\circ}$. The AZtec program was used in $4\times4$ binning mode, with frame averaging over one frame. The step size was 2 $\mu$m for the rugose coral and 1.2 $\mu$m for the brachiopod. The electron beam interacts with the crystal and is diffracted in a characteristic pattern for calcite. The diffracted beam then interacts with the EBSD detector, depdending on the orientation of the calcite crystal. The data were analyzed using software from Oxford instruments.

Rinsed and dried brachiopod flakes were prepared for imaging by coating them with a layer of carbon 12 nm thick. The coated flakes were imaged using a Zeiss 1550VP Field Emission Scanning Electron Microscrope (SEM) under high vacuum using the secondary electron detector. The working distance was $\sim 6$ mm and the electron high tension was 10 kV.

>>>>

While all fossils were inspected under a microscope prior to sampling, we were not able to inspect all fossils in thin section, because carbonate clumped isotope measurements require large amounts of material, some of which is lost during preparation of thin sections. However, 30 $\mu$m-thick uncovered, polished thin sections were obtained from cuts through four representative fossils, two brachiopods and two rugose corals. These thin sections were inspected first in transmitted and reflected light to characterize calcite textures, and were then examined using several different spectroscopic techniques, described below.

@@

Electron backscatter diffraction (EBSD) provides an independent measure of recrystallization by mapping the orientation of calcite crystals in a thin section. This allows more detailed characterization of calcite fabrics than is possible using optical microscopy, and in the case of brachiopods, comparison to pristine modern examples \citep{PerezHuerta2007}. The thin sections were analyzed using a Zeiss 1550VP Field Emission Scanning Electron Microscrope (SEM) under variable pressure vacuum, with an electron high tension of 20 kV. The stage was tilted 70$^{\circ}$. The AZtec program was used in $4\times4$ binning mode, with frame averaging over one frame and a step size of 2 $\mu$m for the rugose coral and 1.2 $\mu$m for the brachiopod. The electron beam interacts with the crystal and is diffracted in a characteristic pattern for calcite. The diffracted beam then interacts with the EBSD detector, depdending on the orientation of the calcite crystal. The data were analyzed using software from Oxford instruments.

Flakes of the secondary fibrous layer from over ten different brachiopods were also imaged to further inspect the preservation of original fibrous calcite texture. The rinsed and dried flakes were prepared for imaging by coating them with a layer of carbon 12 nm thick. The coated flakes were imaged using using the secondary electron detector in the same SEM as above, under high vacuum. The working distance was $\sim 6$ mm and the electron high tension was 10 kV.
